---
title: "simpleRegress"
author: "Emma "
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE, interval= "prediction")
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).



```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

In this plot we can see that the Multiple R squared is bigger in this plot and our adjusted R squared is also slightly bigger by about 0.04. Our residual standard error is 4.9 in this model which is smaller than the plot above which was about 5.3. From this we can say that model 2 is the better model. 



```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```
   
Compared to the first model of NECK and LENGTH, there is some similarities in the residual standard error and adjusted R-squared value. This means both model are about the same and WEIGHT did not give us a significant change to our values. 



```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

  
This model seems to be much better than the previous ones because the residual standard error is smaller and the adjusted R-squared is higher, therefore this is better.  
